---
title: "Lab 02 - Plastic waste"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

First plots are histograms of the distribution of plastic waste per capita faceted by continent.

Second plot is the same data as a density plot.

```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  #To make them one graph by color, add in fill = continent after plastice_waste_per_cap
  geom_histogram(binwidth = 0.2) + facet_wrap(vars(continent))
plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)



ggplot(
  data = plastic_waste,
  mapping = aes(
    x = plastic_waste_per_cap,
    color = continent,
    fill = continent
  )
) +
  geom_density()

```

### Exercise 2

```{r plastic-waste-density}
# insert code here
```

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-mismanaged}
# insert code here
```

```{r plastic-waste-mismanaged-continent}
# insert code here
```

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r recreate-viz}
# insert code here
```


